---
output: github_document
---

# complexR

## Overview

`complexR` is a tool for easily computing and visualizing transformations on 
complex numbers:

- `circle_transform()` performs and visualizes any kind of transformation on 
circles

- `line_transform()` performs and visualizes any kind of transformation on lines
- `quad_transform()` performs and visualizes any kind of transformation on 
squares and rectangles

- `plane_to_sphere()` and `sphere_to_plane()` compute stereographic projections

- `st_sphere_plot()` and `st_plane_plot()` visualize them.

These functions combine other intermediary functions like `cart_to_polar()` and 
`polar_to_cart()` to execute their operations. You can learn more about them in
`vignette("complexR")`. 

## Installation

Use this code to download the development version of `complexR`.

```{r}
devtools::install_github("Swaha294/complexR")
```


## Usage

Visualize the transformation $f(z) = 2xy + iy^2$ on the unit circle centered at (1, 0)

```{r}
library(complexR)
circle_transform(
  x0 = 1, 
  x_new = expression(2*x*y), 
  y_new = expression(y^2),
  annotations = c(complex(real = 2, imaginary = 0), complex(real = 1, imaginary = 1))
  )
```



