---
title: "Introduction to complexR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to complexR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(complexR)
```


When working with the `complexR` package:

* if you are visualizing a transformation, you must:

  + know what domain you are dealing with
  
  + what the real and imaginary elements of your transformation are, i.e., get a 
  transformation function $f(z)$ of the form $f(z) = u(z) + i \cdot v(z)$
  
* if you are computing or visualizing a stereographic projection, you must:

  + know whether you are going from the plane $\mathbb{C}$ to the Riemann sphere
  $\mathbb{C}^*$ or vice versa
  
* if you are computing transformations between polar and Cartesian coordinates,
you must:

  + know what your coordinates are in one form to compute the other form

## Transformations between Coordinates

`complexR` provides functions to:

* transform polar to Cartesian coordinates using `polar_to_cart()`

* transform Cartesian to polar coordinates using `cart_to_polar()`

## Visualizing Transformations

`complexR` provides functions to visualize transformations on the following domains:

* circles using `circle_transform()`

* discs using `disc_transform()`

* squares and rectangles using `quad_transform()`

* squares and rectangles surfaces using `quad_surface_transform()`

* lines using `line_transform()`


## Stereographic Projections

### Computing Stereographic Projections

`complexR` provides functions for:

* computing projections from the complex plane to the Riemann sphere using 
`plane_to_sphere()`

* computing projections from the Riemann sphere to the complex plane using 
`sphere_to_plane()`

### Visualizing Stereographic Projections

`complexR` provides functions for:

* visualizing projections from the complex plane to the Riemann sphere using 
`st_sphere_plot()`

* visualizing projections from the Riemann sphere to the complex plane using 
`st_plane_plot()`
